---
title: "Assignment 0"
author: "Parminder Sandhu - 023700107 (pssandhu3- Github)"
output:
  html_document:
    df_print: paged
  pdf_document: default
  github: pssandhu3
---

ToDo 1
Compute the difference between 2014 and the
year you started at this university and divide
this by the difference between 2014 and the year
you were born. Multiply this with 100 to get
the percentage of your life you have spent at
this university. Use brackets if you need them.

```{r}
((2018-2014)/(2014-1992))*100
```

ToDo 2
Repeat the previous ToDo, but with several
steps in between. You can give the variables
any name you want, but the name has to start
with a letter.

```{r}
a=5
b=4
c=a*b
d=a+b
e=c*d+50-7
e
```

ToDo 3

Compute the sum of 4, 5, 8 and 11 by first combining them into a vector and then using the
function sum.

```{r}
sum(4,5,8,11)
```

ToDo 4
Plot 100 normal random numbers.
```{r}
x= rnorm(100) 
plot(x)
```

ToDo 5
Find help for the sqrt function.
```{r}
help(sqrt)
```

ToDo 6
Make a file called firstscript.R containing Rcode that generates 100 random numbers and
plots them, and run this script several times. 
We can run the script by highlighting the code and pressing control+enter or by control+shift+s
```{r}
plot(rnorm(100))
```

ToDo 7
Put the numbers 31 to 60 in a vector named
P and in a matrix with 6 rows and 5 columns
named Q. Tip: use the function seq. Look at
the different ways scalars, vectors and matrices
are denoted in the workspace window.
```{r}
P = seq(from=31, to=60, by=1)
Q= matrix(P,ncol = 5, nrow = 6)
P
Q

```

ToDo 8
Make a script file which constructs three random normal vectors of length 100. Call these
vectors x1, x2 and x3. Make a data frame called
t with three columns (called a, b and c) containing respectively x1, x1+x2 and x1+x2+x3.
Call the following functions for this data frame:
plot(t) and sd(t). Can you understand the
results? Rerun this script a few times.
```{r}
x1=seq(from=1, to=100, by=1)
x2=seq(from=101, to=200, by=1)
x3=seq(from=201, to=300, by=1)
t= data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
```

ToDo 9
ToDo Add these lines to the script file of the previous section. Try to find out, either by experimenting or by using the help, what the meaning is of rgb, the last argument of rgb, lwd, pch, cex.
```{r}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,col=rgb(0,0,1,0.3))
```

ToDo 10
Make a file called tst1.txt in Notepad from
the example in Figure 4 and store it in your
working directory. Write a script to read it, to
multiply the column called g by 5 and to store
it as tst2.txt.
```{r}
d = data.frame(g = c(3,4,5),h = c(12,43,54))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 = read.table(file="tst1.txt",header=TRUE)
z=d2$g*5
write.table(z,file="tst2.txt")
z
```

ToDo 11
Compute the mean of the square root of a vector of 100 random numbers. What happens?

```{r}
sqrt(mean(rnorm(100)))

```
ToDo 12

```{r}
date1=strptime( c("20190127","20181231","19920605"),format="%Y%m%d")
present=c(10,6,9)
date1
present
plot(date1,present)

```
ToDo 13
Make a vector from 1 to 100. Make a for-loop
which runs through the whole vector. Multiply
the elements which are smaller than 5 and larger
than 90 with 10 and the other elements with 0.1.
```{r}
vector=seq(from=1, to=100, by=1)
q=c()
for(i in 1:100)
{
  if(vector[i]<5 || vector[i]>90)
  {
    q[i]=vector[i]*5;
  }
  else
  {
    q[i]=vector[i]*0.1;
  }
}
q


```
ToDo 14
```{r}
fun= function(arg1,arg2 )
{
  vector[i]=arg1[i];
  for(i in length(vector))
  {
    
  }
}

```
Sources:
https://rmarkdown.rstudio.com/lesson-3.html
https://rmarkdown.rstudio.com/lesson-15.html
https://nicercode.github.io/guides/reports/
http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
